---
title: "Did.the.decline.of.matrilineal.system.relate.to.subsistence.strategy.or.sibling.configuration"
author: "Yaming Huang"
date: "2024-04-16"
output: pdf_document
---

```{r Setup, echo=FALSE, warning=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(dagitty)
library(glmmTMB)
library(emmeans)
library(plyr)
library(dplyr)
library(MuMIn)
library(geepack)
library(ggplot2)
library(dotwhisker)
library(ggalt)
library(rethinking)
options(digits = 12)
# LOAD INHERITANCE AND GIFTS DATA
load("D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Did.the.decline.of.matrilineal.system.relate.to.subsistence.strategy.or.sibling.configuration.RData")

```

## The DAG for inheritance system

We use a directed acyclic graph to identify the cause–effect relationships that we intend to model. For testing the interactions of gender and other variables (cohorts, sibling configuration and subsistence system), our models should been stratified by cohorts, sibling configuration and subsistence system, respectively.

```{r Inheritance system analyses, echo=TRUE}
# DAG of inheritance system ----
DAG_inherit <- dagitty('dag {
"birth order" [pos="-0.876,0.824"]
cohorts [pos="0.067,-1.231"]
gender [exposure,pos="-0.983,-1.220"]
inheritance [outcome,pos="-1.476,-0.078"]
siblings [pos="0.260,0.813"]
subsistence [pos="0.629,-0.122"]
"birth order" -> inheritance
cohorts -> "birth order"
cohorts -> inheritance
cohorts -> siblings
cohorts -> subsistence
gender -> inheritance
siblings -> inheritance
subsistence -> inheritance
}
')

plot(DAG_inherit)


# Build models ----
Inheritance.model.1 <- glmmTMB(Inheritance ~ 1 + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.2 <- glmmTMB(Inheritance ~ Cohort + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.3 <- glmmTMB(Inheritance ~ Gender + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.4 <- glmmTMB(Inheritance ~ Sibling.configuration + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.5 <- glmmTMB(Inheritance ~ Subsistence + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.6 <- glmmTMB(Inheritance ~ Gender + Cohort + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.7 <- glmmTMB(Inheritance ~ Gender + Cohort + 
                                 Sibling.configuration + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.8 <- glmmTMB(Inheritance ~ Gender + Cohort + 
                                 Subsistence + (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())

Inheritance.model.9 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                 Sibling.configuration + Subsistence + 
                                 (1|Mother_ID),
                               data = Inheritance.data,
                               family = binomial())
summary(Inheritance.model.9)
Inheritance.model.9.Conf <- as.data.frame(confint(Inheritance.model.9, level = 0.95))
(Inheritance.model.9.OR <- exp(Inheritance.model.9.Conf))

Inheritance.model.10 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                  Sibling.configuration + Subsistence + 
                                  Cohort : Gender + (1|Mother_ID),
                                data = Inheritance.data,
                                family = binomial())
summary(Inheritance.model.10)
Inheritance.model.10.Conf <- as.data.frame(confint(Inheritance.model.10,level = 0.95))
(Inheritance.model.10.OR_95ci <- exp(Inheritance.model.10.Conf))
Em.inheritance.model.10 <- emmeans(Inheritance.model.10, ~ Cohort : Gender)
contrast(Em.inheritance.model.10, "revpairwise", by="Cohort", adjust="none")
Em.inheritance.model.10.confint <- as.data.frame(confint(contrast(Em.inheritance.model.10, "revpairwise", by="Cohort", adjust="none")))
(Em.inheritance.model.10.confint.OR_95ci <- Em.inheritance.model.10.confint %>%
  mutate(OR = exp(Em.inheritance.model.10.confint$estimate),
         low_ci = exp(Em.inheritance.model.10.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.10.confint$upper.CL)))

Inheritance.model.11 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                  Sibling.configuration + Subsistence +
                                  Sibling.configuration : Gender + (1|Mother_ID),
                                 data = Inheritance.data,
                                 family = binomial())
summary(Inheritance.model.11)
Inheritance.model.11.Conf <- as.data.frame(confint(Inheritance.model.11, level = 0.95))
(Inheritance.model.11.OR_95ci <- exp(Inheritance.model.11.Conf))
Em.inheritance.model.11<- emmeans(Inheritance.model.11, ~ Sibling.configuration : Gender)
contrast(Em.inheritance.model.11, "revpairwise",by="Sibling.configuration",adjust="none")
Em.inheritance.model.11.confint <- as.data.frame(confint(contrast(Em.inheritance.model.11, "revpairwise", by="Sibling.configuration", adjust="none")))
(Em.inheritance.model.11.confint.OR_95ci <- Em.inheritance.model.11.confint %>%
  mutate(OR = exp(Em.inheritance.model.11.confint$estimate),
         low_ci = exp(Em.inheritance.model.11.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.11.confint$upper.CL)))

Inheritance.model.12 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                  Sibling.configuration + Subsistence +
                                  Subsistence : Gender + (1|Mother_ID),
                                data = Inheritance.data,
                                family = binomial())
summary(Inheritance.model.12)
Inheritance.model.12.Conf <- as.data.frame(confint(Inheritance.model.12, level = 0.95))
(Inheritance.model.12.OR_95ci <- exp(Inheritance.model.12.Conf))
Em.inheritance.model.12 <- emmeans(Inheritance.model.12, ~ Subsistence : Gender)
contrast(Em.inheritance.model.12, "revpairwise",by="Subsistence",adjust="none")
Em.inheritance.model.12.confint <- as.data.frame(confint(contrast(Em.inheritance.model.12, "revpairwise", by="Subsistence", adjust="none")))
(Em.inheritance.model.12.confint.OR_95ci <- Em.inheritance.model.12.confint %>%
  mutate(OR = exp(Em.inheritance.model.12.confint$estimate),
         low_ci = exp(Em.inheritance.model.12.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.12.confint$upper.CL)))

Inheritance.model.13 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                  Sibling.configuration + Subsistence +
                                  Cohort : Gender + 
                                  Sibling.configuration : Gender + (1|Mother_ID),
                                data = Inheritance.data,
                                family = binomial())
summary(Inheritance.model.13)
Inheritance.model.13.Conf <- as.data.frame(confint(Inheritance.model.13, level = 0.95))
(Inheritance.model.13.OR_95ci <- exp(Inheritance.model.13.Conf))
Em.inheritance.model.13.1 <- emmeans(Inheritance.model.13, ~ Cohort : Gender)
contrast(Em.inheritance.model.13.1, "revpairwise",by="Cohort",adjust="none")
Em.inheritance.model.13.1.confint <- as.data.frame(confint(contrast(Em.inheritance.model.13.1, "revpairwise", by="Cohort", adjust="none")))
(Em.inheritance.model.13.1.confint.OR_95ci <- Em.inheritance.model.13.1.confint %>%
  mutate(OR = exp(Em.inheritance.model.13.1.confint$estimate),
         low_ci = exp(Em.inheritance.model.13.1.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.13.1.confint$upper.CL)))
Em.inheritance.model.13.2 <- emmeans(Inheritance.model.13, ~ Sibling.configuration : Gender)
contrast(Em.inheritance.model.13.2, "revpairwise",by="Sibling.configuration",adjust="none")
Em.inheritance.model.13.2.confint <- as.data.frame(confint(contrast(Em.inheritance.model.13.2, "revpairwise", by="Sibling.configuration", adjust="none")))
(Em.inheritance.model.13.2.confint.OR_95ci <- Em.inheritance.model.13.2.confint %>%
  mutate(OR = exp(Em.inheritance.model.13.2.confint$estimate),
         low_ci = exp(Em.inheritance.model.13.2.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.13.2.confint$upper.CL)))

Inheritance.model.14 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                  Sibling.configuration + Subsistence +
                                  Gender : Cohort + 
                                  Subsistence : Gender + (1|Mother_ID),
                                data = Inheritance.data,
                                family = binomial())
summary(Inheritance.model.14)
Inheritance.model.14.Conf <- as.data.frame(confint(Inheritance.model.14, level = 0.95))
(Inheritance.model.14.OR_95ci <- exp(Inheritance.model.14.Conf))
Em.inheritance.model.14.1 <- emmeans(Inheritance.model.14, ~ Gender : Cohort)
contrast(Em.inheritance.model.14.1, "revpairwise",by="Cohort",adjust="none")
Em.inheritance.model.14.1.confint <- as.data.frame(confint(contrast(Em.inheritance.model.14.1, "revpairwise", by="Cohort", adjust="none")))
(Em.inheritance.model.14.1.confint.OR_95ci <- Em.inheritance.model.14.1.confint %>%
  mutate(OR = exp(Em.inheritance.model.14.1.confint$estimate),
         low_ci = exp(Em.inheritance.model.14.1.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.14.1.confint$upper.CL)))
Em.inheritance.model.14.2 <- emmeans(Inheritance.model.14, ~ Gender : Subsistence)
contrast(Em.inheritance.model.14.2, "revpairwise",by="Subsistence",adjust="none")
Em.inheritance.model.14.2.confint <- as.data.frame(confint(contrast(Em.inheritance.model.14.2, "revpairwise", by="Subsistence", adjust="none")))
(Em.inheritance.model.14.2.confint.OR_95ci <- Em.inheritance.model.14.2.confint %>%
  mutate(OR = exp(Em.inheritance.model.14.2.confint$estimate),
         low_ci = exp(Em.inheritance.model.14.2.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.14.2.confint$upper.CL)))

Inheritance.model.15 <- glmmTMB(Inheritance ~ Cohort + Gender + 
                                  Sibling.configuration + Subsistence +
                                  Cohort : Gender + 
                                  Sibling.configuration : Gender + 
                                  Subsistence : Gender + (1|Mother_ID),
                                data = Inheritance.data,
                                family = binomial())
summary(Inheritance.model.15)
Inheritance.model.15.Conf <- as.data.frame(confint(Inheritance.model.15, level = 0.95))
(Inheritance.model.15.OR_95ci <- exp(Inheritance.model.15.Conf))
Em.inheritance.model.15.1 <- emmeans(Inheritance.model.15, ~ Cohort : Gender)
contrast(Em.inheritance.model.15.1, "revpairwise",by="Cohort",adjust="none")
Em.inheritance.model.15.1.confint <- as.data.frame(confint(contrast(Em.inheritance.model.15.1, "revpairwise", by="Cohort", adjust="none")))
(Em.inheritance.model.15.1.confint.OR_95ci <- Em.inheritance.model.15.1.confint %>%
  mutate(OR = exp(Em.inheritance.model.15.1.confint$estimate),
         low_ci = exp(Em.inheritance.model.15.1.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.15.1.confint$upper.CL)))
Em.inheritance.model.15.2 <- emmeans(Inheritance.model.15, ~ Sibling.configuration : Gender)
contrast(Em.inheritance.model.15.2, "revpairwise",by="Sibling.configuration",adjust="none")
Em.inheritance.model.15.2.confint <- as.data.frame(confint(contrast(Em.inheritance.model.15.2, "revpairwise", by="Sibling.configuration", adjust="none")))
(Em.inheritance.model.15.2.confint.OR_95ci <- Em.inheritance.model.15.2.confint %>%
  mutate(OR = exp(Em.inheritance.model.15.2.confint$estimate),
         low_ci = exp(Em.inheritance.model.15.2.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.15.2.confint$upper.CL)))
Em.inheritance.model.15.3 <- emmeans(Inheritance.model.15, ~ Subsistence : Gender)
contrast(Em.inheritance.model.15.3, "revpairwise",by="Subsistence",adjust="none")
Em.inheritance.model.15.3.confint <- as.data.frame(confint(contrast(Em.inheritance.model.15.3, "revpairwise", by="Subsistence", adjust="none")))
(Em.inheritance.model.15.3.confint.OR_95ci <- Em.inheritance.model.15.3.confint %>%
  mutate(OR = exp(Em.inheritance.model.15.3.confint$estimate),
         low_ci = exp(Em.inheritance.model.15.3.confint$lower.CL),
         high_ci = exp(Em.inheritance.model.15.3.confint$upper.CL)))

(Model.sel.inheritance <- model.sel(Inheritance.model.1,
                                    Inheritance.model.2,
                                    Inheritance.model.3,
                                    Inheritance.model.4,
                                    Inheritance.model.5,
                                    Inheritance.model.6,
                                    Inheritance.model.7,
                                    Inheritance.model.8,
                                    Inheritance.model.9,
                                    Inheritance.model.10,
                                    Inheritance.model.11,
                                    Inheritance.model.12,
                                    Inheritance.model.13,
                                    Inheritance.model.14,
                                    Inheritance.model.15,
                                    rank = AIC))

(AIC.inheritance <- AIC(Inheritance.model.1,
                        Inheritance.model.2,
                        Inheritance.model.3,
                        Inheritance.model.4,
                        Inheritance.model.5,
                        Inheritance.model.6,
                        Inheritance.model.7,
                        Inheritance.model.8,
                        Inheritance.model.9,
                        Inheritance.model.10,
                        Inheritance.model.11,
                        Inheritance.model.12,
                        Inheritance.model.13,
                        Inheritance.model.14,
                        Inheritance.model.15))

# Plot figures ----
## OR figures-model 10, model 11 and model 12  ----
Inheritance.fig.3models<-data.frame(
  term = c("<=1955","1956-1965","1966-1975",
           "1976-1985","1986-1995",">1995",
           "Equal number","More sisters","More brothers",
           "Farming","Half farming and half pastoral",
           "Pastoral","Non-traditional"),
  estimate = c(Em.inheritance.model.10.confint.OR_95ci$estimate,
               Em.inheritance.model.11.confint.OR_95ci$estimate,
               Em.inheritance.model.12.confint.OR_95ci$estimate),
  std.error = c(Em.inheritance.model.10.confint.OR_95ci$SE,
                Em.inheritance.model.11.confint.OR_95ci$SE,
                Em.inheritance.model.12.confint.OR_95ci$SE),
  OR = c(Em.inheritance.model.10.confint.OR_95ci$OR,
         Em.inheritance.model.11.confint.OR_95ci$OR,
         Em.inheritance.model.12.confint.OR_95ci$OR),
  ORlower = c(Em.inheritance.model.10.confint.OR_95ci$low_ci,
              Em.inheritance.model.11.confint.OR_95ci$low_ci,
              Em.inheritance.model.12.confint.OR_95ci$low_ci),
  ORhigher = c(Em.inheritance.model.10.confint.OR_95ci$high_ci,
               Em.inheritance.model.11.confint.OR_95ci$high_ci,
               Em.inheritance.model.12.confint.OR_95ci$high_ci),
  model = c("Model 10","Model 10","Model 10",
            "Model 10","Model 10","Model 10",
            "Model 11","Model 11","Model 11",
            "Model 12","Model 12","Model 12","Model 12"))
Inheritance.fig.3models$term <- factor(Inheritance.fig.3models$term,
                                       levels = c("<=1955","1956-1965","1966-1975",
                                                  "1976-1985","1986-1995",">1995",
                                                  "Equal number","More sisters","More brothers",
                                                  "Farming","Half farming and half pastoral",
                                                  "Non-traditional","Pastoral"),
                                       labels = c("cohort.1","cohort.2","cohort.3",
                                                  "cohort.4","cohort.5","cohort.6",
                                                  "Equal.number","More.sisters","More.brothers",
                                                  "Farming","Half.farming.and.half.pastoral",
                                                  "Non.traditional","Pastoral"))
Inheritance.fig.3models$model <- factor(Inheritance.fig.3models$model,
                                        levels = c("Model 10","Model 11","Model 12"),
                                        labels = c("Model 10","Model 11","Model 12"))


{{
  dwplot(Inheritance.fig.3models,
         style = "distribution",
         model_name = "Models",
         dot_args = list(size = 1.2),
         dist_args = list(alpha = 0.25),
         line_args = list(alpha = 0.75, size = 0.2),
         vline = geom_vline(xintercept = 0,
                            colour = "grey60",
                            linetype = 2))
}%>% # plot line at zero _behind_ coefs
    relabel_predictors(
      c(cohort.1 = "<=1955: male\n(ref: female)",
        cohort.2 = "1956-1965: male\n(ref: female)",
        cohort.3 = "1966-1975: male\n(ref: female)",
        cohort.4 = "1976-1985: male\n(ref: female)",
        cohort.5 = "1986-1995: male\n(ref: female)",
        cohort.6 = ">=1995: male\n(ref: female)",
        Equal.number = "Equal number: male\n(ref: female)",
        More.sisters = "More sisters: male\n(ref: female)",
        More.brothers = "More brothers: male\n(ref: female)",
        Farming = "Agriculture: male\n(ref: female)",
        Half.farming.and.half.pastoral = "Semi-agriculture, semi-pastoralism: male\n(ref: female)",
        Non.traditional = "Non-traditional industry: male\n(ref: female)",
        Pastoral = "Pastoralism: male\n(ref: female)")
    )+ 
    xlab("Coefficients")+
    scale_x_continuous(limits = c((-2),2),breaks = seq((-2),2,1))+
    scale_colour_brewer(palette = "Set2",
                        name = NULL,
                        breaks = c("Model 12","Model 11","Model 10"),
                        labels = c("Model 12 (best fitting)\nsubsistence * gender",
                                   "Model 11\nsibling configuration * gender",
                                   "Model 10\ncohort * gender"))+
    scale_fill_brewer(palette = "Set2",
                      name = NULL,
                      breaks = c("Model 12","Model 11","Model 10"),
                      labels = c("Model 12 (best fitting)\nsubsistence * gender",
                                 "Model 11\nsibling configuration * gender",
                                 "Model 10\ncohort * gender"))+
    theme(strip.background = element_rect(color = "black", fill = "white"),
          strip.text.x = element_text(size = 16,face = "bold"),
          axis.line = element_line(),
          panel.grid.major = element_line(colour = "Gainsboro"),
          panel.grid.minor = element_blank(),
          panel.border = element_rect(colour="black",fill=NA),
          panel.background = element_blank(),
          legend.position = c(0.99,0.99),
          legend.justification = c(0.99,0.99),
          plot.title = element_text(size=25, family = "serif",face = "bold", hjust = 0),
          axis.title.x = element_text(size = 25,family = "serif",face = "bold",
                                      margin = margin(t = 0.4, r = 0, b = 0, l = 0,unit = "cm")),
          axis.text.x = element_text(colour="black",size=22, family = "serif",face = "bold",
                                     margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
          axis.title.y = element_text(size = 25,family = "serif",face = "bold",
                                      margin = margin(t = 0, r = 0, b = 0, l = 0,unit = "cm")),
          axis.text.y = element_text(colour="black",size=22,family = "serif",face = "bold",
                                     margin = margin(t = 5,b = 5, unit = "pt")),
          legend.title = element_text(size=25,family = "serif",face = "bold"),
          legend.text = element_text(size=18,family = "serif",face = "bold",
                                     margin = margin(t = 10,b = 10, unit = "pt")))
}

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Dot and whisker plot - inheritance models-3.jpeg", width=420, height=340, units="mm")

## Predicted probabilities of inheriting family wealth by cohort and gender----
Pre.inheritance.model.10 <- as.data.frame(predict(Inheritance.model.10, 
                                                  type = "response"))
Pre.inheritance.model.10 <- Pre.inheritance.model.10 %>%
  mutate(Gender = Inheritance.data$Gender,
         Birth.year = Inheritance.data$Birth.year,
         Cohort = Inheritance.data$Cohort)
colnames(Pre.inheritance.model.10) <- c("Predicted.pro",
                                        "Gender","Birth.year",
                                        "Cohort")

ggplot(Pre.inheritance.model.10,
       aes(x = Birth.year, 
           y = Predicted.pro, 
           color = Gender, 
           fill = Gender,
           shape = Gender))+
  geom_point(size = 2.5, alpha = 0.2)+
  geom_smooth(method = "loess", formula = y ~ x,
              alpha = 0.3, 
              span = 0.8,
              se = F, linewidth = 1)+
  geom_ribbon(stat = "smooth",
              method = "loess", formula = y ~ x,
              se = T,
              alpha = 0.3,
              span = 0.8,
              linetype = "dashed")+
  geom_vline(xintercept = c(1955,1965,1975,1985,1995),
             colour = "grey60",
             linetype = 2)+
  labs(x = "Cohort (birth year)",
       y = "Predicted probability of inheritance",
       group = "Gender",
       color = "Gender",
       fill = "Gender",
       shape = "Gender")+
  scale_x_continuous(limits = c(1920,2010),breaks = seq(1920,2010,10))+
  scale_y_continuous(limits = c(0.0,1),breaks = seq(0.0,1,0.2))+
  scale_shape_manual(values = c(16,17))+
  scale_color_manual(values = c("#FA7F6F","#82B0D2"))+
  scale_fill_manual(values = c("#FA7F6F","#82B0D2"))+
  geom_text(x = 1937.5, y = 0.9, 
            aes(label = "Cohort 1 ***"), 
            size = 5, colour = "black",family = "serif",fontface = "bold") +
  geom_text(x = 1960, y = 0.9, 
            aes(label = "Cohort 2 **"), 
            size = 5, colour = "black",family = "serif",fontface = "bold") +
  geom_text(x = 1970, y = 0.9, 
            aes(label = "Cohort 3 ***"), 
            size = 5, colour = "black",family = "serif",fontface = "bold") +
  geom_text(x = 1980, y = 0.9, 
            aes(label = "Cohort 4"), 
            size = 5, colour = "black",family = "serif",fontface = "bold") +
  geom_text(x = 1990, y = 0.9, 
            aes(label = "Cohort 5"), 
            size = 5, colour = "black",family = "serif",fontface = "bold") +
  geom_text(x = 2000, y = 0.9, 
            aes(label = "Cohort 6"), 
            size = 5, colour = "black",family = "serif",fontface = "bold") +
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,family = "serif",face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "white"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        legend.position = c(0.99,0.01),
        legend.justification = c(0.99,0.01),
        plot.title = element_text(size=22,family = "serif",face = "bold"),
        axis.title.x = element_text(size = 22,family = "serif",face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=20,family = "serif",face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 22,family = "serif",face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=20,family = "serif",face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=18,family = "serif",face = "bold"),
        legend.text=element_text(size=18,family = "serif",face = "bold",
                                 margin = margin(t = 10,b = 10, unit = "pt")))

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Gender&BY - inheritor models.jpeg", width=300, height=160, units="mm")

## Predicted probabilities of inheriting family wealth by sibling configuration and gender ----
Pre.inheritance.model.11 <- as.data.frame(predict(Inheritance.model.11, 
                                                  type = "response"))
Pre.inheritance.model.11 <- Pre.inheritance.model.11 %>%
  mutate(Gender = Inheritance.data$Gender,
         Birth.year = Inheritance.data$Birth.year,
         Cohort = Inheritance.data$Cohort,
         Sibling.configuration = Inheritance.data$Sibling.configuration)
colnames(Pre.inheritance.model.11) <- c("Predicted.pro",
                                        "Gender","Birth.year",
                                        "Cohort","Sibling.configuration")

ggplot(data = Pre.inheritance.model.11,
       aes(x = Sibling.configuration, 
           y = Predicted.pro,
           color = Gender,
           fill = Gender))+
  geom_violin(trim = T,
              position = position_dodge(0.6),
              alpha = 0.2)+
  geom_boxplot(width = 0.2,
               position = position_dodge(0.6),
               alpha = 0.4)+
  labs(x = "Sibling configuration",
       y = "Predicted probability of inheritance",
       group = "Gender",
       fill = "Gender")+
  scale_x_discrete(breaks=c("No bias","Sister","Brother"),
                   labels=c("Equal number",
                            "More sisters",
                            "More brothers"))+
  scale_y_continuous(limits = c(0,1),breaks = seq(0,1,0.2))+
  scale_fill_manual(values = c("#ff8884","#9ac9db"))+
  scale_color_manual(values = c("#ff8884","#9ac9db"))+
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,family = "serif",face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "grey90"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        legend.position = "none",
        plot.title = element_text(size=18,family = "serif",face = "bold"),
        axis.title.x = element_text(size = 18,family = "serif",face = "bold",
                                    margin = margin(t = 1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=16,family = "serif",face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 18,family = "serif",face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=16,family = "serif",face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=14,family = "serif",face = "bold"),
        legend.text=element_text(size=14,family = "serif",face = "bold",
                                 margin = margin(t = 10,b = 10, unit = "pt")))

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Gender&sib - inheritor models.jpeg", width=200, height=200, units="mm")

## Predicted probabilities of inheriting family wealth by subsistence and gender ----
Pre.inheritance.model.12 <- as.data.frame(predict(Inheritance.model.12, 
                                                  type = "response"))
Pre.inheritance.model.12 <- Pre.inheritance.model.12 %>%
  mutate(Gender = Inheritance.data$Gender,
         Birth.year = Inheritance.data$Birth.year,
         Cohort = Inheritance.data$Cohort,
         Subsistence = Inheritance.data$Subsistence)
colnames(Pre.inheritance.model.12) <- c("Predicted.pro",
                                        "Gender","Birth.year",
                                        "Cohort","Subsistence")
Pre.inheritance.model.12$Subsistence <- factor(Pre.inheritance.model.12$Subsistence,
                                               levels = c("Non-traditional","Farming",
                                                          "Half farming and half pastoral","Pastoral"),
                                               labels = c("Non-traditional","Farming",
                                                          "Half farming and half pastoral","Pastoral"))

ggplot(data = Pre.inheritance.model.12,
       aes(x = Subsistence, 
           y = Predicted.pro,
           color = Gender,
           fill = Gender))+
  geom_violin(trim = T,
              position = position_dodge(0.6),
              alpha = 0.2)+
  geom_boxplot(width = 0.2,
               position = position_dodge(0.6),
               alpha = 0.4)+
  labs(x = "Subsistence system",
       y = "Predicted probability of inheritance",
       group = "Gender",
       fill = "Gender")+
  scale_x_discrete(breaks=c("Non-traditional","Farming",
                            "Half farming and half pastoral","Pastoral"),
                   labels=c("Non-traditional\n industry","Agriculture",
                            "Semi-agriculture &\n semi-pastoralism","Pastoralism"))+
  scale_y_continuous(limits = c(0,1),breaks = seq(0,1,0.2))+
  scale_fill_manual(values = c("#ff8884","#9ac9db"))+
  scale_color_manual(values = c("#ff8884","#9ac9db"))+
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,family = "serif",face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "grey90"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        legend.position = c(0.99,0.99),
        legend.justification = c(0.99,0.99),
        plot.title = element_text(size=18,family = "serif",face = "bold"),
        axis.title.x = element_text(size = 18,family = "serif",face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=16,family = "serif",face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 18,family = "serif",face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=16,family = "serif",face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=14,family = "serif",face = "bold"),
        legend.text=element_text(size=14,family = "serif",face = "bold",
                                 margin = margin(t = 10,b = 10, unit = "pt")))

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Gender&sub - inheritor models.jpeg", width=200, height=200, units="mm")

## Proportions of five sibling configurations by birth cohorts ----
Sibling.5.cohort.sum <- ddply(Inheritance.data,
                              c("Cohort",
                                "Sibling.configuration.original"), summarise,
                              Num = length(Mother_ID))
Sibling.5.cohort.sum <- as.data.frame(Sibling.5.cohort.sum) %>%
  dplyr::group_by(Cohort) %>%
  dplyr::mutate(Sum = sum(Num)) %>%
  dplyr::mutate(Pro = Num/Sum)
Sibling.5.cohort.sum.row.add <- Sibling.5.cohort.sum[29,]
Sibling.5.cohort.sum <- rbind(Sibling.5.cohort.sum, Sibling.5.cohort.sum.row.add)
Sibling.5.cohort.sum[29,2] <- "More daughters"
Sibling.5.cohort.sum[29,3] <- 0
Sibling.5.cohort.sum[29,4] <- 205
Sibling.5.cohort.sum[29,5] <- 0
Sibling.5.cohort.sum$Cohort.c1 <- c(rep(c(1:6), each = 5))

ggplot(Sibling.5.cohort.sum,
       aes(x = Cohort.c1,
           y = Pro,
           fill = Sibling.configuration.original)) +
  geom_area(alpha = 0.35)+
  scale_x_continuous(breaks = 1:6, 
                     labels = c("<=1955","1956-1965",
                                "1966-1975","1976-1985",
                                "1986-1995",">1995"),
                     expand=c(0, 0))+
  scale_y_continuous(expand=c(0, 0))+
  labs(x = "Cohort",
       y = "Proportion",
       fill = "Fertility")+
  scale_fill_manual(values = c("#fb8072", "#F4A2A3", "#FFBE7A", "#8dd3c7", "#80b1d3"),
                    breaks = c("Only daughters","More daughters",
                               "Equal number",
                               "More sons","Only sons"),
                    labels = c("Only daughters","More daughters",
                               "Equal number",
                               "More sons","Only sons"))+
  geom_text(x = 3.5, y = 0.97, 
            aes(label = "Only daughters"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.75, 
            aes(label = "More daughters"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.50, 
            aes(label = "Equal number"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.25, 
            aes(label = "More sons"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.03, 
            aes(label = "Only sons"), 
            family = "serif",
            size = 6, colour = "black")+
  theme(panel.grid=element_blank(),
        panel.border = element_rect(color = "black", linewidth = 1, fill = NA),
        panel.background=element_rect(color="black", fill='transparent'),
        legend.position = "none",
        axis.title.x = element_text(size = 22,family = "serif",face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=20,family = "serif",face = "bold",
                                   margin = margin(t = 0.3, r = 0, b = 0.1, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 22,family = "serif",face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=20,family = "serif",face = "bold",
                                   margin = margin(t = 0, r = 0.3, b = 0, l = 0,unit = "cm")),
        plot.margin = margin(t = 10,r = 30,b = 2,l = 5))

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Sib_5&BY.jpeg", width=270, height=180, units="mm")

## Proportions of four main household livelihood forms by birth cohorts ----
Subsistence.cohort.sum <- ddply(Inheritance.data, 
                                c("Cohort","Subsistence"), summarise, 
                                Num = length(Mother_ID))

Subsistence.cohort.sum <- as.data.frame(Subsistence.cohort.sum) %>%
  dplyr::group_by(Cohort) %>%
  dplyr::mutate(Sum = sum(Num)) %>%
  dplyr::mutate(Pro = Num/Sum)
Subsistence.cohort.sum.row.add <- Subsistence.cohort.sum[23,]
Subsistence.cohort.sum <- rbind(Subsistence.cohort.sum,Subsistence.cohort.sum.row.add)
Subsistence.cohort.sum[23,2] <- "Pastoral"
Subsistence.cohort.sum[23,3] <- 0
Subsistence.cohort.sum[23,4] <- 205
Subsistence.cohort.sum[23,5] <- 0
Subsistence.cohort.sum$Cohort.c1 <- c(rep(c(1:6), each = 4))

ggplot(Subsistence.cohort.sum,
       aes(x = Cohort.c1,
           y = Pro,
           fill = Subsistence)) +
  geom_area(alpha = 0.35)+
  scale_x_continuous(breaks = 1:6, 
                     labels = c("<=1955","1956-1965",
                                "1966-1975","1976-1985",
                                "1986-1995",">1995"),
                     expand=c(0, 0))+
  scale_y_continuous(expand=c(0, 0))+
  labs(x = "Cohort",
       y = "Proportion",
       fill = "Subsistence system")+
  scale_fill_manual(values = c("#fb8072", "#FFBE7A", "#8dd3c7", "#80b1d3"),
                    breaks = c("Farming","Half farming and half pastoral",
                               "Pastoral","Non-traditional"),
                    labels = c("Agriculture","Semi-agriculture & semi-pastoralism",
                               "Pastoralism","Non-traditional industry"))+
  geom_text(x = 3.5, y = 0.85, 
            aes(label = "Agriculture"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.35, 
            aes(label = "Semi-agriculture and semi-pastoralism"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.12, 
            aes(label = "Pastoralism"), 
            family = "serif",
            size = 6, colour = "black")+
  geom_text(x = 3.5, y = 0.04, 
            aes(label = "Non-traditional industry"), 
            family = "serif",
            size = 6, colour = "black")+
  theme(panel.grid=element_blank(),
        panel.border = element_rect(color = "black", linewidth = 1, fill = NA),
        panel.background=element_rect(color="black", fill='transparent'),
        legend.position = "none",
        axis.title.x = element_text(size = 22,family = "serif",face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=20,family = "serif",face = "bold",
                                   margin = margin(t = 0.3, r = 0, b = 0.1, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 22,family = "serif",face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=20,family = "serif",face = "bold",
                                   margin = margin(t = 0, r = 0.3, b = 0, l = 0,unit = "cm")),
        plot.margin = margin(t = 10,r = 30,b = 2,l = 5))

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Sub&BY-area.jpeg", width=270, height=180, units="mm")

```

## The DAG for gifts received

We also use a directed acyclic graph to identify the cause–effect relationships that we intend to model. From the results, we should include the age, dispersal pattern, gender of egos, the age and dispersal pattern of alters, and study times into models in order to test the direct effects of gender on the amount of money received.

```{r Gifts received analyses, echo=TRUE}
# DAG of gifts received ----
DAG_gift <- dagitty('dag {
bb="0,0,1,1"
"alter age" [pos="0.343,0.912"]
"alter dispersal pattern" [pos="0.089,0.566"]
"alter economy" [pos="0.170,0.759"]
"alter education" [pos="0.112,0.313"]
"alter gender" [exposure,pos="0.194,0.145"]
"ego age" [pos="0.653,0.906"]
"ego dispersal pattern" [pos="0.913,0.561"]
"ego economy" [pos="0.828,0.749"]
"ego education" [pos="0.889,0.340"]
"ego gender" [pos="0.772,0.143"]
"gifts received" [outcome,pos="0.500,0.403"]
"survey period" [pos="0.498,0.028"]
"alter age" -> "alter dispersal pattern"
"alter age" -> "gifts received"
"alter dispersal pattern" -> "gifts received"
"alter economy" -> "gifts received"
"alter education" -> "gifts received"
"alter gender" -> "alter dispersal pattern"
"alter gender" -> "gifts received"
"ego age" -> "alter gender"
"ego age" -> "gifts received"
"ego dispersal pattern" -> "alter dispersal pattern"
"ego dispersal pattern" -> "gifts received"
"ego economy" -> "gifts received"
"ego education" -> "gifts received"
"ego gender" -> "alter gender"
"ego gender" -> "gifts received"
"survey period" -> "alter gender"
"survey period" -> "gifts received"
}
')

plot(DAG_gift)

# Build models ----
Gifts.model.1 <- geeglm(No.money ~ 1,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.2 <- geeglm(No.money ~ From.age.scale,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.3 <- geeglm(No.money ~ From.phi.place,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.4 <- geeglm(No.money ~ From.gender,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.5 <- geeglm(No.money ~ To.age.scale,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.6 <- geeglm(No.money ~ To.phi.place,
                        id = From.ID, family="poisson",
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.7 <- geeglm(No.money ~ Time,
                        id = From.ID, family="poisson",
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.8 <- geeglm(No.money ~ To.gender,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.9 <- geeglm(No.money ~ From.age.scale + 
                          From.phi.place + 
                          From.gender + 
                          To.age.scale + 
                          To.phi.place + 
                          To.gender + Time,
                        id = From.ID, family="poisson", 
                        data = Gifts.dyad, 
                        corstr="exchangeable", scale.fix = T)

Gifts.model.10 <- geeglm(No.money ~ From.age.scale + 
                          From.phi.place + 
                          From.gender + 
                          To.age.scale + 
                          To.phi.place + 
                          To.gender * Time,
                         id = From.ID, family="poisson", 
                         data = Gifts.dyad, 
                         corstr="exchangeable", scale.fix = T)
summary(Gifts.model.10)$coefficients

Model.sel.gifts.model <- MuMIn::model.sel(Gifts.model.1,
                                          Gifts.model.2,
                                          Gifts.model.3,
                                          Gifts.model.4,
                                          Gifts.model.5,
                                          Gifts.model.6,
                                          Gifts.model.7,
                                          Gifts.model.8,
                                          Gifts.model.9,
                                          Gifts.model.10,
                                          rank = "QIC")
Model.sel.gifts.model
(QIC.all <- QIC(Gifts.model.1,
               Gifts.model.2,
               Gifts.model.3,
               Gifts.model.4,
               Gifts.model.5,
               Gifts.model.6,
               Gifts.model.7,
               Gifts.model.8,
               Gifts.model.9,
               Gifts.model.10))

Em.gifts.model.10 <- emmeans(Gifts.model.10, ~ Time * To.gender)
contrast(Em.gifts.model.10, "revpairwise", by="Time", adjust="none")
Em.Gifts.model.10.confint <- as.data.frame(confint(contrast(Em.gifts.model.10, "revpairwise", by="Time", adjust="none")))
(Em.Gifts.model.10.confint.OR_95ci <- Em.Gifts.model.10.confint %>%
  mutate(OR = exp(Em.Gifts.model.10.confint$estimate),
         low_ci = exp(Em.Gifts.model.10.confint$asymp.LCL),
         high_ci = exp(Em.Gifts.model.10.confint$asymp.UCL)))
Gifts.model.10.coef <- as.data.frame(MuMIn::coefTable(Gifts.model.10))
(Gifts.model.10.IRR_95ci <- Gifts.model.10.coef %>% 
  mutate(IRR = exp(Gifts.model.10.coef$Estimate),
         lowconf = Gifts.model.10.coef$Estimate-
           1.96*Gifts.model.10.coef$`Std. Error`,
         lowCI = exp(Gifts.model.10.coef$Estimate-
                       1.96*Gifts.model.10.coef$`Std. Error`),
         highconf = Gifts.model.10.coef$Estimate+
           1.96*Gifts.model.10.coef$`Std. Error`,
         highCI = exp(Gifts.model.10.coef$Estimate+
                        1.96*Gifts.model.10.coef$`Std. Error`)))

# Plot figures ----
## Predicted gifts received in dyads ----
Pre.gifts.model <- as.data.frame(predict(Gifts.model.10, full = T,
                                         type = "response"))
Pre.gifts.model <- Pre.gifts.model %>%
  mutate(Gender = Gifts.dyad$To.gender,
         Time = Gifts.dyad$Time)
colnames(Pre.gifts.model) <- c("Predicted.Money",
                               "Gender",
                               "Time")
Pre.gifts.model$Time <- factor(Pre.gifts.model$Time,
                               levels = c("2015","2021"),
                               labels = c("Study-1 (2015)",
                                          "Study-2 (2021)"))

Pre.gifts.model$To.ID <- Gifts.dyad$To.ID

Pre.gifts.model.sum <- ddply(Pre.gifts.model, .(Time,Gender), summarise, 
                           N = length(unique(To.ID)),
                           mean = mean(Predicted.Money), 
                           sd = sd(Predicted.Money))
Pre.gifts.model.sum <- mutate(Pre.gifts.model.sum,
                            Conf.low = mean - sd,
                            Conf.high = mean + sd)

Pre.gifts.model.figure <- 
  ggplot(Pre.gifts.model.sum,aes(x = Time, 
                                 y = mean, 
                                 group = Gender,
                                 colour = Gender))+
  geom_errorbar(aes(ymin = Conf.low, 
                    ymax = Conf.high),
                linewidth = 1.0, width = 0.10, 
                position = position_dodge(0.4))+
  geom_point(size = 3, position = position_dodge(0.4))+
  labs(x = "Studies", 
       y = "Prediced gifts")+
  scale_x_discrete(breaks = c("Study-1 (2015)","Study-2 (2021)"),
                   labels = c("Study-1 (2015)","Study-2 (2021)"))+
  scale_y_continuous(limits = c(0.0020,0.0140),breaks = seq(0.0020,0.0140,0.0010))+
  ##2015
  geom_segment(x = 0.9, y = 0.0111920 + 0.00030, 
               xend = 0.9 , yend = 0.0111920 + 0.00060,
               colour = "black", linewidth = 0.8)+
  geom_segment(x = 0.9, y = 0.0111920 + 0.00060,
               xend = 1.1, yend = 0.0111920 + 0.00060,
               colour = "black", linewidth = 0.8) +
  geom_segment(x = 1.1, y = 0.0111920 + 0.00060 ,
               xend = 1.1, yend = 0.0052797 + 0.00030,
               colour = "black", linewidth = 0.8) +
  geom_text(x = 1, y = 0.0111920 + 0.00090, 
            aes(label = "***"), fontface = "bold",size = 8, colour = "black")+
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "Gainsboro"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        legend.position = c(0.99,0.99),
        legend.justification = c(0.99,0.99),
        plot.title = element_text(size=18,face = "bold"),
        axis.title.x = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=16,face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=16,face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=14,face = "bold"),
        legend.text=element_text(size=12,face = "bold"))
Pre.gifts.model.figure 

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Gifts.model.pre.gender&time.jpeg", width=150, height=150, units="mm")


```


```{r Figures in supplementary materials, echo=TRUE}
# Self-reported main category of each household’s expense  ----
Main.expense <- 
  ggplot(Main.household.expense,
         aes(x = Categories,
             y = Proportion,
             fill = Categories))+
  geom_bar(position = "dodge",stat = "identity")+
  ylim(0,1)+
  labs(x = "Categories",y = "Proportion")+
  scale_x_discrete(breaks=c("Production","Education",
                            "Medicine","Cranes","Tibetan house"),
                   labels=c("Production","Education",
                            "Medicine","Cranes","Tibetan house"))+
  scale_fill_manual(name="Categories",
                    values = c("#DCDCDC","#C5C5C5","#AEAEAE",
                               "#969696","#696969"),
                    breaks = c("Production","Education",
                               "Medicine","Cranes","Tibetan house"),
                    labels = c("Production","Education",
                               "Medicine","Cranes","Tibetan house"))+
  geom_text(x = 5, y = 0.66, 
            aes(label = "61.11%"), 
            fontface = "bold",
            size = 6, 
            colour = "black")+
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "Gainsboro"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        legend.position = "None",
        plot.title = element_text(size=18,face = "bold"),
        axis.title.x = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=14,face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=14,face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=12,face = "bold"),
        legend.text=element_text(size=12,face = "bold"))
Main.expense
ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\Gender&sib - inheritor models.jpeg", width=200, height=200, units="mm")


# Proportion of each economic sources across years in administrative town ----
Ethno.data.economy.figure <- 
  ggplot(data = Economic.sources,
         aes(x = Year, 
             y = Proportion,
             group = Economic.sources,
             colour = Economic.sources,
             fill = Economic.sources)) + 
  geom_point(size = 3, alpha = 0.7)+
  geom_xspline(spline_shape = -0.4, 
               size = 3, alpha = 0.7)+
  xlab("Year")+
  ylab("Proportion")+
  labs(group = "Economic sources")+
  scale_x_continuous(limits = c(2000,2015),
                     breaks = seq(2000,2015,5))+
  scale_y_continuous(limits = c(0.0,1),
                     breaks = seq(0.0,1,0.2))+
  scale_colour_manual(name = "Economic sources",
                      values = c("#fb8072", "#8dd3c7", "#80b1d3"))+
  scale_fill_manual(name = "Economic sources",
                    values = c("#fb8072", "#8dd3c7", "#80b1d3"))+
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "Gainsboro"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        legend.position = c(0.99,0.99),
        legend.justification = c(0.99,0.99),
        plot.title = element_text(size=18,face = "bold"),
        axis.title.x = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=16,face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=16,face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=14,face = "bold"),
        legend.text=element_text(size=12,face = "bold"))

Ethno.data.economy.figure
ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\Ethno.data.economy.jpeg", width=200, height=100, units="mm")

# Proportions of household income by economic types and study times ----
Household.income.15_21.figure <- 
ggplot(data = Household.income.15_21,
       aes(x = Year, 
           y = Proportion,
           fill = Types))+
  geom_boxplot(alpha = 0.3)+
  xlab("Years")+
  ylab("Proportion")+
  scale_x_discrete(breaks=c("2015","2021"),
                   labels=c("2015","2021"))+
  scale_y_continuous(limits = c(0,1),breaks = seq(0,1,0.1))+
  scale_fill_manual(name = "",
                    values = c("#fb8072", "#8dd3c7", "#80b1d3"))+
  theme(strip.background = element_rect(color = "black", fill = "white"),
        strip.text.x = element_text(size = 16,face = "bold"),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_line(colour = "Gainsboro"),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(colour="black",fill=NA),
        panel.background = element_blank(),
        plot.title = element_text(size=18,face = "bold"),
        legend.position = "none",
        axis.title.x = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0.3, r = 0, b = 0, l = 0,unit = "cm")),
        axis.text.x = element_text(colour="black",size=16,face = "bold",
                                   margin = margin(t = 0.1, r = 0, b = 0, l = 0,unit = "cm")),
        axis.title.y = element_text(size = 18,face = "bold",
                                    margin = margin(t = 0, r = 0.5, b = 0, l = 0,unit = "cm")),
        axis.text.y = element_text(colour="black",size=16,face = "bold",
                                   margin = margin(t = 0, r = 0.1, b = 0, l = 0,unit = "cm")),
        legend.title=element_text(size=14,face = "bold"),
        legend.text=element_text(size=12,face = "bold"))

Household.income.15_21.figure

ggsave(filename="D:\\Shangri-La\\shangri-la data analyses\\give gift\\separate data by interview year\\paper\\15vs21 economy.jpeg", width=180, height=180, units="mm")

```
